Data Preparation

### 2021-07-13 x0_data-preparation.Rmd
added new_scale_colour

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(zoo)

@@

tmp %>%
  ggplot() +
  geom_line(aes(x = DATE, y = N), colour = "grey80") +
  geom_line(aes(x = DATE, y = N_sm, colour = THRES2, group = "RQ"), size = 2) +
  geom_line(aes(x = DATE, y = UP_THR), color = "blue") +
  geom_line(aes(x = DATE, y = LOW_THR), color = "red") +
  geom_line(aes(x = DATE, y = MED), color = "green") +
  geom_line(aes(x = DATE, y = BAND, group= "1"), colour = if_else(tmp$LOW_CRIT, "red","green"), size = 4) +
  geom_line(aes(x = DATE, y = BAND-500, group= "1"), colour = if_else(tmp$UP_CRIT, "red","green"), size = 4) +
  geom_line(aes(x = DATE, y = BAND-1500, group= "1", colour = STATE), size = 4) +
  theme_minimal() +
  theme(legend.position = "none")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages("ggnewscale")
library(tidyverse)
library(lubridate)
library(zoo)
library(ggnewscale)

@@

###---------Rainer, the "new_scale_colour()" kinda resets the scale, and you can use another one for the next geom_lines. In the example below, I left the legend.position = "bottom" (instead of "NULL"), just to see the colors------###
tmp %>%
  ggplot() +
  geom_line(aes(x = DATE, y = N), colour = "grey80") +
  geom_line(aes(x = DATE, y = N_sm, colour = THRES2, group = "RQ"), size = 2) +
  geom_line(aes(x = DATE, y = UP_THR), color = "blue") +
  geom_line(aes(x = DATE, y = LOW_THR), color = "red") +
  geom_line(aes(x = DATE, y = MED), color = "green") +
  scale_color_brewer(type = "seq") +
  new_scale_colour() +
  geom_line(aes(x = DATE, y = BAND, group= "1"), colour = if_else(tmp$LOW_CRIT, "red","green"), size = 10) +
  geom_line(aes(x = DATE, y = BAND-500, group= "1"), colour = if_else(tmp$UP_CRIT, "red","green"), size = 4) +
  geom_line(aes(x = DATE, y = BAND-1500, group= "1", colour = STATE), size = 4) +
  scale_colour_brewer(type = "qual") +
  theme_minimal() +
  theme(legend.position = "bottom")
```
